Empirical Bayes analysis for detection of gene heterosis in RNAseq data

### 2014-12-17 ebayes_rnaseq_heterosis.tex
comment and little edit to readme

% Need to udpate as this is directly from Tieming's paper
Heterosis, or hybrid vigor, refers to the enhances phenotype of hybrid progeny relative to their inbred parents. Taking maize as an example, the offspring from crossing the inbred lines B73 and Mo17 are taller, mature faster, and produce greater yields than their parent lines \citep{hallauer1981quantitative, hallauer2010quantitative}. Since heterosis was scientifically documented by \cite{darwin1876effects}, it has been successfully manipulated to improve many species for food, feed, and fuel industries, such as rice \citep{yu1997importance}, alfalfa \citep{riday2002heterosis}, tomatoes \citep{krieger2010flowering}, and fish \citep{wohlfarth1993heterosis}. Despite the intensive study and successful utilization of heterosis, the basic genomic mechanisms remain unclear \citep{coors1999genetics, lippman2007heterosis}. Researchers speculate that gene-expression heterosis could be among the mechanisms responsible for the phenotypic heterosis \citep{swanson2006all, springer2007allelic}.

>>>>

% Need to udpate as this is directly from Tieming's paper
Heterosis, or hybrid vigor, refers to the enhances phenotype of hybrid progeny relative to their inbred parents. Taking maize as an example, the offspring from crossing the inbred lines B73 and Mo17 are taller, mature faster, and produce greater yields than their parent lines \citep{hallauer1981quantitative, hallauer2010quantitative}. Since heterosis was scientifically documented by \cite{darwin1876effects}, it has been successfully manipulated to improve many species for food, feed, and fuel industries, such as rice \citep{yu1997importance}, alfalfa \citep{riday2002heterosis}, tomatoes \citep{krieger2010flowering}, and fish \citep{wohlfarth1993heterosis}. Despite the intensive study and successful utilization of heterosis, the basic genomic mechanisms remain unclear \citep{coors1999genetics, lippman2007heterosis}. Researchers speculate that gene-expression heterosis $-$ i.e, enhanced expression of one or more genes in the hybrid relative to the inbred parents $-$ could be among the mechanisms responsible for the phenotypic heterosis \citep{swanson2006all, springer2007allelic}.

% WL: Since you mainly talk about phenotypic heterosis, I added a little clarification about gene-expression heterosis. However, the reader will still be mostly focused on phenotypic heterosis, and more may need to be done to refocus on the transcriptome. Do we have good real-world examples of heterosis in the expression important or interesting genes? This may be a good question for Dan.
